### 2016-07-08 constsampshort.tex
Chandru's shortened version

%!TEX root =  autocontgrlp.tex
\section{Constraint sampling}
One way to reduce the number of constraints is to randomly choose a subset of them \cite{CS},
leading to the so-called reduced linear program (RLP). \todoc{How about the results of Calafiore and Campi (2005, Math. Prog.) and others reviewed in \cite{CS}? Any follow-up we missed?}
While the objective function of the RLP is the same as that of the ALP, 
the RLP has only $m \ll nd$ constraints sampled from the original ALP according to a given probability distribution:
\begin{align}\label{rlp}
\begin{split}
\min_{r\in \N}\, &c^\top \Phi r\\
\text{s.t.}\mb &(\Phi r)(s)\geq g_a(s)+\alpha\sum_{s'}p_a(s,s')(\Phi r)(s'), \mb (s,a) \in \I\,,
\end{split}
\end{align}
where $\I$ is the index set containing $m$ sampled state-action pairs and
the extra constraint set $\N\subset \R^k$ is introduced to guarantee a bounded feasible set (hence, bounded solution).
It is assumed that $\N$ is compact and $\tr\in \N$. \todoc{How can one arrange for this in general?}
The index set $\I$ naturally gives rise to the definition of an $nd\times m$ constraint sampling matrix $\M$:
\begin{definition}\label{csampmat}
Let $\I=\{(s_1,a_1),\ldots,(s_m,a_m)\}$ be the sampled state-action pairs and let $q_i \eqdef s_i+(a_i-1)\times n$, $i=1,\ldots,m$. Define the constraint sampling matrix $\M \in \R^{nd\times m}$ associated with the index set $\I$ by
\begin{align}
\M(i,j)
=
\begin{cases}
1, & \text{ if } q_i = j\,;\\
0, & \text{ otherwise}.
\end{cases}
\end{align}
\end{definition}
The RLP can then be represented in short as
\begin{align}\label{rlpshort}
\begin{split}
\min_{r\in \N}\, &c^\top \Phi r\\
\text{s.t.}\mb & \M^\top E \Phi r \geq \M^\top H \Phi r\,.
\end{split}
\end{align}
Note that apart from $r\in \N$ the feasible set of the RLP is a superset of the feasible set of the ALP.

The RLP based on constraint sampling has been found to perform well empirically in application domains ranging from controlled queuing networks (see section $6.2$ of \cite{ALP} and section $7$ of \cite{SALP}) to Tetris (see \cite{CST} and section $6$ of \cite{SALP}). However, the theoretical guarantees for the RLP are available only under a restricted setting \cite{CS}. We present the main result of \cite{CS} on constraint sampling, and to that end define the following quantities:
%\begin{definition}\label{sampdist}
Given a policy $u$, a Lyapunov function $\psi$ in the column span of $\Phi$
and a probability distribution $c$ over the states
we define probability distributions $\mu_{u,c}$, $\mu_{u,c,\psi}$ and constant $\theta_{u,c,\psi}$ as 
\begin{align}
\mu_{u,c}^\top& \eqdef (1-\alpha)c^\top (I-\alpha P_u)^{-1},\nn\\
\mu_{u,c,\psi}(s,a)&\eqdef (d \, \mu_u^\top \psi)^{-1} \, \mu_{u}(s) \psi(s),\nn\qquad s\in \S,a\in  \A\,,\\
\theta_{u,c,\psi} &\eqdef\mfrac{(1+\beta_{\psi})}{2} \, \mfrac{\mu_{u,c}^\top \,\psi}{\norm{J^*}_{1,c}}\, \sup_{r\in \N}||J^*-\Phi r||_{\mn}.
\end{align}
%\end{definition}
Note that in the definition of $\theta_{u,c,\psi}$ the \emph{supremum} 
of the error of approximating $J^*$ by the LFA over $\N$ appears.
De Farias and Van Roy show through an example how this term can still be reasonable controlled  \cite{CS}.
\todoc{If we avoid this, this would be great!}

We now recall Theorem~$3.1$ of \cite{CS} below. \todoc{Assumptions? }
\begin{theorem}\label{csresult}
Let $\epsilon$ and $\delta$ be scalars in $(0,1)$,
$\theta = \theta_{u^*,c,\psi}$ where $u^*$ is an optimal policy.
Let $\I$ be an index set obtained by sampling $m$ state-action pairs 
	independently according to the distribution $\mu_{u^*,c,\psi}$,
	\todoc{Their Lyapunov function definition is slightly different. Which one is the real one needed by this result?}
	where%
	\footnote{Note that the cardinality of $\I$ might be smaller than $m$.}
\begin{align}
m\geq \frac{16d\theta}{(1-\alpha)\epsilon}\left(k\ln\frac{48d\theta}{(1-\alpha)\epsilon}+\ln\frac{2}{\delta}\right).
\end{align}
Let $\tilde{r}_c$ be an optimal	solution of the ALP and let $\hat{r}_c$ be the solution of the corresponding RLP. 
Assume that $\tilde{r}_c\in \N$.
Then, with probability at least $1-\delta$, we have
\begin{align}
||J^*-\Phi \hat{r}_c||_{1,c}\leq ||J^*-\Phi \tilde{r}_c||_{1,c}+\epsilon||J^*||_{1,c}.
\end{align}
\end{theorem}
\noindent \textbf{Motivation for our work:}
As noted by the authors of \cite{CS}, this result is best viewed as a
	theoretical illustration of the potential of constraint sampling:
	sampling from $\mu_{u^*,c,\psi}$ will more often than not be infeasible in practice
	as this distribution is dependent on the optimal policy $u^*$.
However, as mentioned before, the RLP has performed reasonably well 
	even when the sampling distribution is not $\mu_{u^*,\psi}$. 
Thus there is a gap between the theoretical understanding of the RLP 
	and its practical efficacy which merits our attention. 
The gap also indicates that the RLP might be a special case 
	of a generalized constraint reduction scheme with provable performance guarantees. 
Understanding such a generalized method would result in an ALP based ADP technique 
	that would have theoretical performance guarantees while being practically useful. 
In particular, we wish to answer the following open questions.
\begin{itemize}
\item  As a natural generalization of the RLP, what happens if we define a generalized reduced linear program (GRLP) whose constraints are positive linear combinations of the original constraints of the ALP?
\item Unlike \cite{CS} which provides error bounds for a specific RLP formulated using an idealized sampling distribution, is it possible to provide error bounds for any GRLP (and hence any RLP)?
\end{itemize}
In this paper, we address both of the questions above.

>>>>

%!TEX root =  autocontgrlp.tex
\section{Constraint sampling}
One way to reduce the number of constraints is to randomly choose a subset of them \cite{CS},
leading to the so-called reduced linear program (RLP). \todoc{How about the results of Calafiore and Campi (2005, Math. Prog.) and others reviewed in \cite{CS}? Any follow-up we missed?}
While the objective function of the RLP is the same as that of the ALP, 
the RLP has only $m \ll nd$ constraints sampled from the original ALP according to a given probability distribution:
\begin{align}\label{rlp}
\min_{r\in \N}\, &c^\top \Phi r\nn\\
\text{s.t.}\mb &(\Phi r)(s)\geq g_a(s)+\alpha\sum_{s'}p_a(s,s')(\Phi r)(s'), \nn\\
&\forall (s,a) \in \I.
\end{align}
where $\I$ is the index set containing $m$ sampled state-action pairs and the extra constraint set $\N$ is introduced to guarantee a bounded solution. Note that apart from $r\in \N$ the feasible set of the RLP is a superset of the feasible set of the ALP. 
\begin{comment}
The index set $\I$ in \eqref{rlp} naturally gives rise to the definition of an $nd\times m$ constraint sampling matrix $\M$:
\begin{definition}\label{csampmat}
Let $\I=\{(s_1,a_1),\ldots,(s_m,a_m)\}$ be the sampled state-action pairs and let $q_i \eqdef s_i+(a_i-1)\times n$, $i=1,\ldots,m$. Define the constraint sampling matrix $\M \in \R^{nd\times m}$ associated with the index set $\I$ by
\begin{align}
\M(i,j)
=
\begin{cases}
1, & \text{ if } q_i = j\,;\\
0, & \text{ otherwise}.
\end{cases}
\end{align}
\end{definition}
The RLP can then be represented in short as
\begin{align}\label{rlpshort}
\begin{split}
\min_{r\in \N}\, &c^\top \Phi r\\
\text{s.t.}\mb & \M^\top E \Phi r \geq \M^\top H \Phi r\,.
\end{split}
\end{align}
The error bounds for the RLP can be found in \cite{CS} and the RLP has been shown to perform well in experiments \cite{ALP,CS,CST} in various domains such as Tetris and in network of queues. An alternative to constraint sampling is to introduce function approximation in the dual variables of the ALP \cite{ALP-Bor,dolgov}. While such an approach has been applied in practice, there are no known theoretical guarantess for function approximation of the dual variables.\par
In the next section, we present the generalized reduced linear program (GRLP) which is the main object of study in this paper.
\end{comment}

### 2016-07-08 grlp.tex
polishing
Chandru's shortened version

%!TEX root =  autocontgrlp.tex
\section{Generalized Reduced Linear Program}
In this section we present the generalized reduced linear program (GRLP) which is obtained by replacing the set of sampled constraints in the RLP by a set of constraints which are obtained as linear combinations of the original constraints of the ALP. Formally, we define the generalized reduced linear program (GRLP) as follows:
\begin{align}\label{grlp}
\begin{split}
\underset{r\in \N}{\min}\, &\, c^\top \Phi r,\\
\text{s.t.}\mb & \,W^\top E\Phi r\geq W^\top H \Phi r, 
\end{split}
\end{align}
where $W \in \R_+^{nd\times m}$ is an $nd\times m$ matrix with all nonnegative entries and 
$\N \subset \R^k$ is a set such that $\tilde{r}_c \in \N$. 
\todoc{Changed the definition and using $\N$ that was used in the definition of RLP.}
The role of $\N$, as in the case of RLPs, is to guarantee
the existence of bounded solutions. \todoc{We'll be trouble with $\N$ if we start assume that it is a bounded set. See below.}

The $i^{th}$ ($1\leq i\leq m$) constraint of the GRLP is a positive linear combination of the original constraints of the ALP. Constraint reduction is achieved by choosing $m\ll nd$. The key difference between the RLP in \eqref{rlpshort} and the GRLP in \eqref{grlp} despite their similar structure is that while $\M$ is a matrix of only zeros and ones, $W$ is a matrix of positive entries alone. Also note that an RLP is trivially a GRLP as well with a random matrix $W$. Unless specified otherwise, we use $\hr$ to denote any solution to the GRLP in \eqref{grlp}, $\hj=\Phi \hr$, to denote the corresponding approximate value function and $\hu$ to denote the greedy policy with respect to $\hj$.\par
Note that we want to avoid certain uninteresting and trivial cases of $W$ matrix such as $W=0$ or an entire column of $W$ being zero (which means no constraint is generated with respect to that column). Thus it is intuitive to demand that every column of $W$ should be non-negative and have at least one entry which is strictly positive. Then, normalizing the columns of $W$ so that they sum to $1$ does not make any difference to the constraints of the RLP. Keeping these in mind we also assume the following throughout the rest of the paper:
\begin{assumption}\label{wassump}
$W \in \R^{nd\times m}_+$ is a full rank $nd\times m$  matrix (where $m\ll nd$) and each of its column-sums equals one.
\end{assumption}
\begin{comment}
The above assumption is just a technical condition that eliminates uninteresting choices such as $W=0$ or cases when certain columns of $W$ have all zeros, which implies that the corresponding column generates no constraint.
\end{comment}
\input{cartoon}
\todoc{The picture needs to be perfected.}
The rest of the paper develops analytically various performance bounds and our main results provide the following:
\begin{enumerate}
\item A bound for $||J^*-\hj||$, the error between the approximate value function $\hj$ as computed by the GRLP and the optimal value function $J^*$;
\item a bound for $||J^*-J_{\hu}||$, the loss in performance due to the greedy policy $\hu$ measured with respect to the optimal policy; and
\item an important result on constraint sampling. \todoc{we should be more specific}
\end{enumerate}
We achieve the above via two novel $\max$-norm contraction operators namely the least upper bound (LUB) projection operator (denoted by $\Gamma$) and the approximate least upper bound (ALUB) projection operator (denoted by $\hat{\Gamma}$). We bound the error due to constraint approximation by analyzing the fixed points of the operators $\Gamma$ and $\hg$. We first establish our results in the $L_\infty$-norm and then in a weighted $L_\infty$-norm. The schematic in Fig.~\ref{schematic} provides a pictorial representation of what shall follow in the next three sections.
\FloatBarrier
\input{schematic}
\todoc{$d_1$ and $d_2$ use different norms?}

>>>>

%!TEX root =  autocontgrlp.tex
\section{Generalized Reduced Linear Program}
\begin{assumption}\label{grlpassmp}
\begin{enumerate}[(i)]
\item \label{probdist} $c=(c(i),i=1,\ldots,n)\in \R^n$ is a positive probability distribution, i.e., $c(i)>0 \mb \forall i$ and $\sum_{i=1}^n c(i)=1$.
\item  \label{one} The first column of the feature matrix $\Phi$ (i.e., $\phi_1$) is $\one \in \R^n$. 
\item \label{lyap} $\psi\colon S \ra \R_+$ is a Lyapunov function for $P$
and is present in the column span of the feature matrix $\Phi$: For some $r_0\in \R^k$, $\Phi r_0 = \psi$. 
\item \label{nassmp} $\N\subset \R^k$ is compact and $\tr \in \N\subset\R^k$.
\item \label{wassump} $W \in \R^{nd\times m}_+$ is a full rank $nd\times m$ matrix (where $m\ll nd$), with all non-negative entries such that each of its column-sums equals one.
\item \label{ass:n4} The set $\N'$ is such that $\N' = \N + t r_0$ for any $t\in \R$, where $r_0\in \R^k$ such that $\Phi r_0 = \psi$.
\end{enumerate}
\end{assumption}
When \cref{grlpassmp}-\eqref{lyap} holds, it follows that for any $J\in \R^n$, $t>0$, $s\in S$,
\begin{align}
\label{eq:psilin}
T(J+ t \psi ) \le TJ + \beta_{\psi}\,t\,  \psi\,\, \quad (J\in \R^n,\, t>0)\,.
\end{align}
The approximate linear program (ALP) is obtained by making use of LFA in the LP, i.e., by adding the extra constraint $J=\Phi r$ in \eqref{mdplp} with $\Phi \in \R^{n\times k}$ and introducing the new variables $r\in \R^k$. By substitution, this leads to
\begin{align}\label{alp}
\begin{split}
\min_{r\in \R^k}\, &c^\top \Phi r\\
\text{s.t.}\mb &\Phi r\geq T \Phi r,
\end{split}
\end{align}
where $J\geq TJ$ is a shorthand for the $nd$ constraints in \eqref{mdplp}. Unless specified otherwise we use $\tr$ to denote any solution to the ALP, $\tj=\Phi \tr$ to denote the corresponding approximate value function and $\tu$ to denote the greedy policy with respect to $\tj$.
The Generalized Reduced Linear Program is given as:
\begin{align}\label{grlp}
\begin{split}
\underset{r\in \N}{\min}\, &\, c^\top \Phi r,\\
\text{s.t.}\mb & \,W^\top E\Phi r\geq W^\top H \Phi r,
\end{split}
\end{align}
where $W \in \R^{nd\times m}_+$ is a matrix with all positive entries and $\N$ is an additional constraint set to ensure the boundedness of the solution.
In what follows, we denote the solution to the GRLP by $\hr$, the approximate value function by $\hj=\Phi \hr$ and use $\hu$ to denote the greedy policy with respect to $\hj$.

### 2016-07-08 intro.tex
Chandru's shortened version

%!TEX root =  autocontgrlp.tex
\section{Introduction}\label{intro}
Optimal sequential decision making problems occurring in science, engineering and economics can be cast in the framework of Markov Decision Processes (MDPs). A policy $u$, is a mapping from state space to action space and it specifies the action selection mechanism. The problem of \emph{control} requires coming up with good policies and for which one needs to \emph{predict} the behavior of individual policies. The problem of \emph{prediction} deals with computing the value-function $J_u$(a mapping from state space to reals\footnote{Also known as reward/cost-to-go function.}) which specifies the value of each state under a given policy $u$. \todoc{How is the MDP given? If it is given as a list of values, just reading the values may take too much time.
Or we assume sparsity? Or we assume that one can query the next state distribution at any state-action? These yield to different models. We should specify which one we work with (presumably the sparse is the easiest).
}Ideally, we are be interested in computing the optimal value function $J^*$ and the optimal policy $u^*$. The Bellman equation (BE) relates these quantities and in particular $u^*$ can be obtained as a `greedy/one-step look ahead' policy by substituting $J^*$ in the BE. Conventional solution methods for MDPs \cite{BertB} such as value iteration, policy iteration and linear programming can compute exact values of $J^*$ and $u^*$ by either directly or indirectly solving the Bellman equation. By computing $J^*$ and $u^*$, the conventional methods address both the prediction and control problems. However, in the case of MDPs with large number of states, computing $u^*$ and $J^*$ using the exact methods is infeasible. \todoc{Do we have a source to cite here? What does it mean to solve an MDP anyways? Find an optimal policy? Find a near-optimal policy? I think the story is that knowing the optimal value function helps, but I have not seen any claim that it is \emph{necessary} to compute it to find.}

\emph{Approximate dynamic programming} (ADP) \cite{dpchapter,powell} refers to a gamut of approximate solution methods to MDPs with large number of states. Value-function-only\footnote{Since this paper is concerned with results related to the approximate linear programming formulation we do not discuss other classes of ADP methods such as \emph{actor-only} and \emph{actor-critic} methods.} (or \emph{critic-only}) ADP methods compute an approximate value function and use it to obtain a one-step look ahead policy by making use of BE. In order to reduce the computational effort, the approximate value function is restricted to a chosen parametrized class of functions. The most widely used parametrization to approximate the value function is the \emph{linear function approximator} (LFA). Methods employing LFA approximate the value function as $\Phi r^*$, where $\Phi$ is a feature matrix whose columns are the basis functions and $r^*$ is a weight vector to be learned. Computational advantage (in terms of the number of unknowns) is achieved by choosing fewer number of basis functions compared to the number of states. Once the set of basis function is chosen, the way to compute $r^*$ varies across the different ADP methods.\todoc{I don't understand why one should care about  approximating $J^*$ at all.}

A host of value-function-based ADP methods solve the \emph{projected Bellman equation} (PBE) which is obtained by including the least squares projection operator in the BE so as to project quantities onto the lower dimensional subspace. A limitation of using the least squares projection operator is that it reduces the prediction error $L_2$-norm and cannot ensure policy improvement which requires prediction error to be minimum in the $L_\infty$-norm. Due to this norm mismatch, policy improvement cannot be guaranteed and \emph{policy-chattering} (policy-oscillations) can occur in practice \cite{dpchapter}. As a result, the performance loss is difficult to control and existing result that control this loss are proven under restrictive conditions \cite{anszemu:mlj07,FaMuSz10}.

The \emph{approximate linear programming} (ALP) \cite{ALP,CS,SALP,ALP-Bor,gkp,fs,npalp} formulation also employs LFA, however, solves a linear program to compute $J^*\approx\tilde{J}=\Phi r^*$, and computes a one-step greedy policy $\tilde{u}$. Since ALP computes an approximation to $J^*$ and outputs only a single policy $\tilde{u}$, there is no issue of policy-chattering. The ALP formulation also provides theoretical performance guarantees, i.e., the prediction error $||J^*-\tilde{J}||$ and the control error\footnote{loss in performance due to the sub-optimal policy} $||J^*-J_{\tilde{u}}||$ can be bounded. This makes ALP an attractive method since it addresses both the prediction and control problems by providing the error bounds. However, an important shortcoming of ALP is that the number of constraints are of the order of the state space, making the vanilla version of ALP intractable.

One proposal in the literature to overcome this hurdle is to employ a procedure known as constraint sampling, wherein a subset of the original constraints of the ALP are sampled to formulate a \emph{reduced linear program} (RLP). The RLP has been shown to perform well in experiments \cite{ALP,CS,CST} in various domains such as Tetris and in network of queues. However, the theoretical results are available only for a specific RLP formulated under idealized conditions \cite{CS}. Thus, there is a gap in the theoretical understanding of RLP and constraint reduction/approximation. Our aim in this paper is to fill this gap by providing theoretical guarantees which will make the RLP a complete ADP method that addresses both the prediction and the control problems.

In particular, in this paper we develop a novel theoretical framework to study a generalized constraint reduction technique namely \emph{generalized reduced linear program} (GRLP) and present its error analysis. The salient aspects of our contribution are listed below:
\begin{enumerate}
\item \textbf{Framework:}

We generalize RLPs to define GRLPs. A GRLP has a small number of constraints which are obtained as positive linear combinations of the original constraints of the ALP. 
The GRLP serves as a framework to analyze error due to constraint reduction and linear constraint approximation.
\item \textbf{Error Analysis:}
	\begin{itemize}
		\item We develop novel analytical machinery to relate $\hat{J}$, the solution to the GRLP, and the optimal value function $J^*$. 
		\item We show a bound of the form $||J^*-\hat{J}||\leq c_1+c_2$, 
		where the term $c_1$ is the error inherent to the ALP formulation itself, 
		while the term $c_2$ is the additional error introduced due to the constraint approximation.  
		\item We derive a greedy policy $\hu$ by making use of $\hj$ and bound the loss $||J^*-J_{\hu}||$. 
		\item Akin to the error analysis in \cite{ALP,CS,SALP} our bounds are also in terms of a modified $L_\infty$-norm.
		\item Our analysis is based on two novel $\max$-norm contraction operators called the least upper bound (LUB) projection operator and the approximate least upper bound projection operator (ALUB). This is another significant difference in comparison to the results on constraint sampling in \cite{SALP,CS} that make use of concentration bounds and hold only with \emph{high} probability.
\end{itemize}
\item \textbf{Significant Results:}
	\begin{itemize}
		\item We provide error bounds for both prediction and control errors, i.e., bound the terms $||J^*-\hj||$ and $||J^*-J_{\hu}||$ in a modified $L_\infty$-norm. Thus, the GRLP is a complete ADP method with performance guarantees for both the prediction as well as control problems. The modified $L_\infty$-norm allows us to choose the quality of approximation across various states. This makes our result an important addition to the theory of ALP \cite{ALP,CS,CST,SALP}.
		\item The structure of the error terms also reveals an important result that it is not always necessary to sample using the stationary distribution of the optimal policy. This throws additional light on constraint sampling by providing a better explanation for its empirical success even in those cases when sampling distributions other than the stationary distribution of the optimal policy was used. 
		\item Our results on the GRLP are the first to theoretically justify linear function approximation of the constraints. This means that constraint reduction is not only limited to sampling but also can be extended to include linear combinations of constraints.
	\end{itemize}
\item We also discuss the implication of our results in the context of reinforcement learning and also present a numerical example illustrating the theory developed. A short and preliminary version of this paper without the theoretical analysis is available in \cite{aaaipaper}.
\end{enumerate}

>>>>

\section{Introduction}
Markov decision processes (MDPs) is an important mathematical framework to study optimal sequential decision making problems that arise in science and engineering. Solving an MDP involves computing the optimal \emph{value-function} ($J^*$), a vector whose dimension is the number of states. MDPs with small number of states can be solved easily by conventional solution methods such as value / policy iteration or linear programming (LP) \cite{BertB}. Dynamic programming is at the heart of all the conventional solution methods for MDPs.\par
A practical way to tackle the issue of large number of states is to compute an approximate value function $\tilde{J}$ instead of $J^*$. Here, success depends on the quality of approximation, i.e., on the quantity $||J^*-\tilde{J}||$. The most widely used method for approximation is the linear function approximation (LFA), i.e., let $\tilde{J}=\Phi r^*$, where $\Phi$ is a feature matrix and $r^*$ is a learnt weight vector. Dimensionality reduction is achieved by choosing $\Phi$ to have fewer columns in comparison to the number of states and this makes computing $\tilde{J}$ easier.\par
The \emph{approximate linear program} (ALP) \cite{ALP,CS,SALP,ALP-Bor} and its variants introduce linear function approximation in the linear programming formulation. A critical shortcoming of the ALP is that the number of constraints are of the order of the size of the state space, making the vanilla version of the ALP intractable. A way out is to employ a procedure known as constraint sampling, wherein a subset of the original constraints of the ALP are sampled to formulate a \emph{reduced linear program} (RLP). The performance analysis of the RLP can be found in \cite{CS} and the RLP has also been shown to perform well in experiments \cite{ALP,CS,CST}. An alternative approach to handle the issue of large number of constraints is to employ function approximation in the dual variables of the ALP \cite{ALP-Bor,dolgov}, an approach useful in practice, however, without any theoretical guarantees bounding the loss in performance resulting from such an approximation.\par
In this paper, we generalize the RLP to define a generalized reduced linear program (GRLP) which has a tractable number of constraints obtained as positive linear combinations of the original constraints of the ALP. 
The salient aspects of our contribution are listed below:
\begin{enumerate}
		\item We develop novel analytical machinery to relate $\hat{J}$, the solution to the GRLP, and the optimal value function $J^*$ by bounding the prediction erorr $||J^*-\hj||$ (\Cref{cmt2mn}). 
		\item We also bound the performance loss due to the one-step greedy policy $\hu$ (greedy with respect to $\hj$) given by $||J^*-J_{\hu}||$ (Theorem~\ref{polthe}).
		\item Our analysis is based on two novel $\max$-norm contraction operators and our results hold \emph{with probability one}. This is another significant difference in comparison to the results on constraint sampling in \cite{SALP,CS} that make use of concentration bounds and hold only with \emph{high} probability.
		\item Our results on the GRLP are the first to theoretically justify linear function approximation of the constraints.
		\item We demonstrate via an example in controlled queues that the experiments conform to the theory developed.
\end{enumerate}
